Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-27 pirouette_article.tex
Process feedback @Giappo: shortened code, only one library call

{\bf Keywords:} Bayesian model selection, BEAST2, computational biology, evolution, phylogenetics, R, tree prior

@@

\giovanni{
  Do we need the library calls in the listing?
}
\richel{
  I simplified the code and only call pirouette now. 
  I think this is cleaner then using a scope operator.
}
\begin{lstlisting}[language=R]
library(pirouette)

>>>>

{\bf Keywords:} Bayesian model selection, BEAST2, computational biology, evolution, phylogenetics, R, tree prior, babette

@@

\begin{lstlisting}[language=R]
library(pirouette)
